Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
comment on figure 10
revised caption for fig 1

% COMMENTING PREVIOUS WORK AND DEFINITIONS
\iffalse
\subsection{Definitions}
A pattern, or a patch, is a beat-chroma pattern taken from an actual song.
A codeword (sometimes just code) is similar to a pattern, but is the result 
of the clustering
algorithm and most likely does not come from an actual song.
Distortion is our measure of distance between a pattern and a code
(or between two patterns, see equation \ref{eq:dist} in Section 
\ref{sec:experiments}).

@@

\begin{figure}[thb]
\begin{center}
\includegraphics[width=.6\columnwidth]{code}
\end{center}
\caption{\small{A typical codeword from a codebook of size $200$ (code
    7 in Figure \ref{fig:codes1})
Patterns represented
$2$ bars and the pattern length was set to $8$.
}}
\label{fig:code}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{codes_8bars}
\end{center}
\caption{\small{Sample of longer codewords spanning over $8$ bars. Codewords
selected randomly from the codewords used in the test set. Percentage of
use display in parentheses.
Most patterns are sustained notes, but code 0 shows a repeating two chord
pattern.
}}
\label{fig:codes8bars}
\end{figure}

>>>>

% COMMENTING PREVIOUS WORK AND DEFINITIONS
\iffalse
\subsectionDefinitions}
A pattern, or a patch, is a beat-chroma pattern taken from an actual song.
A codeword (sometimes just code) is similar to a pattern, but is the result 
of the clustering
algorithm and most likely does not come from an actual song.
Distortion is our measure of distance between a pattern and a code
(or between two patterns, see equation \ref{eq:dist} in Section 
\ref{sec:experiments}).

@@

\begin{figure}[thb]
\begin{center}
\includegraphics[width=.6\columnwidth]{code}
\end{center}
\caption{\small{A typical codeword from a codebook of size $200$ (code
    7 in Figure \ref{fig:codes1}), corresponding to a
    tonic-subdominant chord progression.  The patch is composed of $2$
    bars and the pattern length was set to $8$ beats.  }}
\label{fig:code}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{codes_8bars}
\end{center}
\caption{\small{Sample of longer codewords spanning over $8$
    bars. Codewords selected randomly from the codewords used in the
    test set. Percentage of use display in parentheses.  Most patterns
    consist of sustained note or chords, but code 0 shows a repeating
    two chord pattern and code 4 contains two bars of a
    1$\rightarrow$1$\rightarrow$1$\rightarrow$2 progression.}}
\label{fig:codes8bars}
\end{figure}
